When are Fuzzy Extractors Possible?

### 2014-06-04 trunk/info-bounds/FuzzyExtPossibility.tex
adding notes about necessary number of sketches for flat distributions

\begin{definition}
Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
\end{definition}

@@

Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).  Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.  Thus, the remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log c - \omega(\log n)
\]
For a flat distribution with a fixed number of neighbors, 
\begin{align*}
\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
\end{align*}
Thus, the construction is optimal up to a super-logarithmic factor~(for flat sources with a fixed number of neighbors).
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\begin{definition}
Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
%In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
\end{definition}

@@

Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).  Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.  Thus, the remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log c - \omega(\log n)
\]
For a flat distribution with a fixed number of neighbors, 
\begin{align*}
\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
\end{align*}
Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.

\subsection{Flat Sources with Sketches that Write a Fixed Number of Bits}
We begin by trying to remove the restriction that every point in the metric space has a fixed number of neighbors in a distribution.  We start with sketches that write down a fixed number of bits~(independent of their input $w$).   We will show a lower bound on the number of bits that a $\sketch$ algorithm must write down.  We assume that all coins of $\sketch$ are provided to $\rec$ and that $\rec$ is deterministic~(any coins needed for $\rec$ can be flipped by $\sketch$ in this model).

\begin{lemma}
Let $W$ be a flat distribution and let $(\sketch, \rec)$ be a secure sketch for $W$.  Let $W$ be a $(c, t)$-bounded neighbor distribution.  Let $S_{coin}$ be the number of sketches that can be produced by any fixing of $coin$.  Then the error $\delta$ of $(\sketch, \rec)$ is at least $\frac{\expe_{coins}L(coins)}{c}$.  
\end{lemma}
\begin{proof}
We consider a fixed $w'$ that has $c$ neighbors in the distribution.  We assume $\rec$ has access to all coins of $\sketch$.  Furthermore, we assume that $\rec$ is deterministic and that any coins necessary are provided by $\sketch$).

Denote by $S_{coin, R}$ the set of possible sketches for a given set of coins on all values in $R$.  Furthermore, denote by $S_{coin}$ the set of possible sketches for all values $w$~(for a given value of coin) and note that $S_{coin, R} \subset S_{coin}$.  Then $\rec(\cdot, w', coin)$ must fail to recover $|R|-|S_{coin, R}|$ fraction of $w\in R$~(recalling that $\rec$ is deterministic for this fixing of $coin$).  This means that the total number of pairs $(w, coin)$ for which $\rec$ fails to recover is $2^{|coins|}R - \sum_{coins} |S_{coin, R}|$.

This means there must exist some $w$ such that the number of $coin$ values for which $\rec$ fails to recover is 
\[
2^{|coin|} - \frac{\sum_{coin} |S_{coin, R}|}{R}.
\]
 This means that for this $w$, 
\[
\Pr_{coin}[s \leftarrow \sketch(w, coin) \wedge w = \rec(s, w', coin)] < 1- \frac{\expe |S_{coin, R}|}{|R|} = 1-\frac{\expe |S_{coin, R}|}{c} \le 1-\frac{\expe |S_{coin}| }{c}.
\]

%Consider the function $\rec(w', ss, r)$ where $ss$ is the sketch produced by $\sketch(w)$ and $r$ are the coins used by $\sketch$.  
\end{proof}

For deterministic sketches:
\[
\Hav(W|S ) = -\log \left(\sum_{s\in S} \Pr[S = s] \frac{2^{-\Hoo(W)}}{\Pr[S=s]}\right) = -\log \left(2^{-\Hoo(W)} |S| \right)  = \Hoo(W) - H_0(S).
\]
\bibliographystyle{alpha}
\bibliography{crypto}
